\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Afonso Pinto Cardoso Rafael} % Your name

% You can merge both of these into a single line, if you do not have a website.
\address{
  \href{mailto:afonsorafael@sapo.pt}{afonsorafael@sapo.pt} /
  \href{https://alf0nso.github.io/}{website} /
  \href{https://www.linkedin.com/in/afonsorafael/}{linkdin} /
  \href{https://github.com/Alf0nso}{github}
}

\begin{document}

%----------------------------------------------------------------------------------------
%	INTERESTED IN
%----------------------------------------------------------------------------------------

%% \begin{rSection}{Interests}
%%   {- Compiler development and functional languages.} \\
%%   {- Type theory and PLT.} \\
%%   {- Quantum Computing.}
%% 
%% \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\bf Masters in Computer Science},
  Faculty of Sciences of the University of Lisbon (dropout)
  \hfill {} \\
  - Relevant Coursework: Compilation Techniques,
  Domain Specific Languages, Quantum Computing.

  {\bf B.S. in Geospatial Engineering},
  Faculty of Sciences of the University of Lisbon
  \hfill {2016 ‑ 2020}

  {\bf Drumming},
  International Drum Academy
  \hfill {2016 ‑ 2020}
  
%  {\bf High School}, Colégio de São Tomas
%  \hfill {2004 ‑ 2016}
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS	
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}
  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming languages &
    Haskell, C, C++, Lisp, Typescript, Python \\
    Technical Skills & Compiler design and implementation, Web Development, Data processing \\
    Soft Skills &
    Enjoy speaking with people, Enjoy presentations and public speaking \\
%%    Music Skills &
%%    Drummer (5 years), Guitarist (6 years), Amateur choir
  \end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE	
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

  \textbf{Junior Research Engineer} \hfill Nov 2023 - Now\\
  Barcelona Supercomputing Center \hfill \textit{Barcelona, ES}
  \begin{itemize}
    \itemsep -3pt {}
  \item Work on fine tuning optimizations in LLVM.
  \item Help fight back against bit rotting.
  \end{itemize}
  
  \textbf{Web Developer} \hfill July 2023 - Nov 2023\\
  Digital MZN \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {}
  \item Help with the development of the arms website (React Native \& Typescript).
  \item Help maintain python environments of other members of the company.
  \end{itemize}
  
  \textbf{Software Developer (Freelancing)} \hfill April 2023 - May 2023\\
  Bynd \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {}    
  \item Build a web crawler in python to collect data on companies to
    be displayed on dashboard.
  \item Using selenium as a dependency to allow interaction between the
    crawler and the web page.
  \end{itemize}

  \textbf{Researcher (Intern)} \hfill September 2022 - March 2023\\
  IMDEA Software \hfill \textit{Madrid, ES}
  \begin{itemize}
    \itemsep -3pt {}
  \item Build relational benchmarks for Liquid Haskell, a compiler plugin that extends Haskell’s type system with refinement types.
  \item Wrote a paper section describing the benchmarks.
  \item Contributed with solving a bug in liquid-fixpoint    (\href{https://github.com/ucsd-progsys/liquid-fixpoint/pull/626}{Pull Request})
  \end{itemize}
  
  \textbf{Research Fellowship} \hfill January 2022 - July 2022\\
% Faculty of Sciences of the university of Lisbon
  LASIGE \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {}
  \item \href{http://rss.di.fc.ul.pt/tryit/FreeST}{Freest} is a functional programming language
    that uses session types for safer communication.
  \item Developed a compiler for the Freest language, targeting JavaScript (Built with Haskell).
  \item Built a test suite for the compiler.
  \item \href{https://alf0nso.github.io/docs/FreeSTwebCompiler.pdf}{Best Poster} - 1st, LASIGE Workshop'22.
  \end{itemize}

  \textbf{Summer with science (Research Fellowship)} \hfill August 2021 \\
  LASIGE \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Built programs with Freest that later got into the testing suite.
  \item Found bugs and reporting them during development.
  \end{itemize}

  \textbf{Software Developer (Intern)} \hfill 2019 - 2020 \\
  Think Future \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Built a system to manage aerial information for control of drone flight (Python).
  \end{itemize}

  \textbf{Data Science (Intern)} \hfill August 2019 - September 2019 \\
  ITC Faculty of Geo‑information Science and Earth Observation \hfill \textit{Ensched, NL}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Wrote data processing code using Dask, an open-source Python library for parallel computing.
  \item Lectured practical classes on the Institute.
  \item Processed geographical information for decision making.
  \end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
% Honors & Awards	
%----------------------------------------------------------------------------------------

%% \begin{rSection}{Honors \& Awards}
%%   \begin{itemize}
%%   \item \href{https://alf0nso.github.io/Alf0nso/mposter/}{Best Poster} - 1st, LASIGE Workshop'22.
%%   \end{itemize}
%% \end{rSection}

%----------------------------------------------------------------------------------------
% Presentations
%----------------------------------------------------------------------------------------

% \begin{rSection}{Presentations}
%   \begin{itemize}
%   \item \href{https://www.youtube.com/watch?v=p7FrTaukioI&t=2693s}{Eu uso Emacs, roast me.} - DevPT - First Meetup.
%   \end{itemize}
% \end{rSection}

%----------------------------------------------------------------------------------------
% Extra-Curricular Activities	
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities}

  \textbf{Discord Admin/Event Manager} \hfill 2020 - Present \\
  DevPT \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Participated in the devPT talks as Manager.
  \item Participated in the devPT as Speaker (\href{https://www.youtube.com/watch?v=p7FrTaukioI&t=2693s}{Eu uso Emacs, roast me.})
  \item Moderate and Help make decisions on the Discord platform.
  \item Help manage social media.
  \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Music}
%  \vspace{-1.25em}

  \textbf{Drummer} \hfill 2019 - 2023 \\
  AZMA \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Play drums and help compose the songs.
  \item Help manage the social accounts and project contacts.
  \item Participated on the recording of songs like: \href{https://www.youtube.com/watch?v=5XqsTF8x76Y}{Akadom}
  \end{itemize}

  \textbf{Guitarist} \hfill 2022 ‑ 2023 \\
  Split Objects \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Support guitarist for the band.
  \item Help with gigs.
  \end{itemize}

  \textbf{Drummer} \hfill 2017 ‑ 2019 \\
  PodPop \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Played drums and helped compose music.
  \item Helped record the video clips.
  \item Participated on the recording of songs like: \href{https://www.youtube.com/watch?v=9566jWHH9QU}{Is It Love Or Sacrifice},
    \href{https://www.youtube.com/watch?v=P65iTaV80Ps}{BlackOut},
    \href{https://www.youtube.com/watch?v=w3lSOWdkliA}{Spoon Of The Gods}.
  \end{itemize}

  \textbf{Guitarist} \hfill 2016 \\
  Why Knot \hfill \textit{Lisbon, PT}
  \begin{itemize}
    \itemsep -3pt {} 
  \item Played guitar and helped compose music.
  \item Participated on the recording of songs like: \href{https://www.youtube.com/watch?v=YBZZrDuIRKo}{Nothing Concrete}.
  \end{itemize}  
\end{rSection} 

\end{document}
